\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-29 OaklandSubmission/ld.tex
till correctness

Most of the expression forms $\widetilde{e}$ are same as $e$, except
that the binary operators, and the conditional forms
are annotated with labels $\ell$, denoting how the operators should be
evaluated ($\mathcal{P}$ for in-clear, $\mathcal{A}$ for arithmetic circuits, and
$\mathcal{B}$ for boolean circuits). The
form $\widetilde{e} \rhd m$ denotes coercing the value of $\widetilde{e}$ to be
$m$-secret shared, which is useful for share-conversions between boolean and arithmetic and also for sharing public values. 
%The statements $\widetilde{s}$ are analogous to $s$.

@@

As mentioned earlier, the intermediate language models the code such as in \figureref{ex-aby} output by our compiler. 
Next, a program in the intermediate language is evaluated to a circuit that can be executed in the distributed setting later. The evaluation to a circuit computes away the public parts of the program and also \emph{flattens} the arrays so that the circuits are unaware of the array structure. 
Crucially, this phase of the semantics does not have access to the secrets.
Below, we first provide the language for the circuits used followed by our evaluation rules.

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{mult}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \bval \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    %\ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Can we merge base value and circuit gate?}}
\label{fig:circuits}
\end{figure}

\subsubsection*{Circuits}
\figureref{circuits} shows the circuits syntax. A wire id range
$\wire$ denotes a set of circuit wires that carry the value of a secret
shared variable in the output circuit (we will concretely define these
values later as part of the circuit semantics). Circuit gates $\gate$
are $\wire$, input gates, \kw{mult}, \kw{gt}, and \kw{mux} gates, and
coerce gates $\bval \rhd m$. \divya{Gates are not just gates but a circuit?} Target values $\val$
then consist of base values $c$ and $\gate$, and arrays of base
values. \\

@@

    \inferrule*[lab={\footnotesize{S-Read}}]
               {
                 \widetilde{\rho} \vdash x \Downarrow [\overline{\wire_i}]_{n_{1}} \\\\
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow n \quad n < n_{1}
               }
               {
                 \widetilde{\rho} \vdash x[\widetilde{e}] \Downarrow \bval_n
               }\\\\
    \inferrule*[lab={\footnotesize{S-SMult}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \gate_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} \mulop_{\mathcal{A}} \widetilde{e_{2}} \Downarrow \kw{mult}\:\gate_{1}\:\gate_{2}
               }

@@

\subsubsection*{Evaluation to Circuit} \figureref{eval-inter-circ} shows the judgments for the evaluation of the intermediate language to a circuit. 
The runtime environment is defined as follows:

\vspace{0.2cm}
$
\small
\begin{array}{rrcl}
    \ftext{Runtime environment} & \widetilde\rho &::=& \cdot \mid \rho,x \mapsto \val\\
\end{array}
$
\vspace{0.2cm}

We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow\val$. 
%
Rules ({\sc{S-PMult}}) and ({\sc{S-SMult}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PMult}}) evaluates a public multiplication $\widetilde{e_{1}}
\mulop_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} \mulop n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SMult}}) evaluates a secret multiplication $\widetilde{e_{1}}
\mulop_{\mathcal{A}} \widetilde{e_{2}}$ to an arithmetic multiplication
gate $\kw{mult}\:\gate_{1}\:\gate_{2}$. As mentioned above, the intermediate language
expressions generated by our compiler never have $\widetilde{e_{1}}
\mulop_{\mathcal{B}} \widetilde{e_{2}}$, as our compiler is aware that $\mulop$
is more performant using an arithmetic circuit compared to a boolean
one. Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along the similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the value from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a \kw{mux} gate that takes input
circuits from the guard ($\gate_{1}$) and both the branches
($\gate_{2}$ and $\gate_{3}$). Once again for performance reasons,
the target expressions from our compiler do not have
$\lcond{\mathcal{A}}{e_{1}}{e_{2}}{e_{3}}$. Rules
({\sc{S-Coerce}}) and ({\sc{S-Inp}}) evaluate to the coerce and input
gates respectively.

Statement evaluation $\widetilde{\rho} \vdash \widetilde{s} \Downarrow
\widetilde{\rho}_{1}; \chi$ evaluates statements $\widetilde{s}$ to produce a new
environment $\widetilde{\rho}_{1}$, and a circuit $\crct$. A circuit $\crct$ (shown
in \figureref{circuits}) is either empty, \kw{bind}-ing of a
circuit gate $\gate$ to wire $\wire$, \kw{out} gate, or a sequence of
circuits. Rules ({\sc{S-DeclC}}), ({\sc{S-DeclCkt}}), and
({\sc{S-DeclCktA}}) show the variable declaration cases. Rule
({\sc{S-DeclC}}) shows the case when $\widetilde{e}$ evaluates to
$\val$, where $\val$ is either a constant or an
array of constants. In this case, the mapping $x \mapsto
\val$ is added to the environment, and the resulting circuit
is empty. When 
$\widetilde{e}$ evaluates to a circuit $\gate$, rule
({\sc{S-DeclCkt}}) picks a fresh wire $\wire$, adds the mapping $x \mapsto \wire$
to the environment $\widetilde{\rho}$, and outputs the circuit
$\kw{bind}\:\gate\:\wire$. Rule ({\sc{S-DeclCktA}}) is analogous for
$\widetilde{e}$ evaluating to an array of circuits. The variable
assignment rules (not shown in the figure) are similar. Rule
({\sc{S-WriteCkt}}) shows the case for writing to an array, where the
array contents are secret. Finally, rule ({\sc{S-Out}}) compiles to an
\kw{out} circuit.

\subsubsection*{Circuit semantics} Evaluating a program in the intermediate language produces a
circuit over the secret data to be computed using an \mpc protocol in the distributed setting. With
our circuit semantics, we model the \emph{functional} aspect of a \mpc protocol, parametrized by the sharing functions.

During the circuit evaluation, the wire ranges $r$ are
mapped to (random) strings $b$. The semantics of these strings is
given by pairs of encode-decode algorithms, written as
$\mathcal{E}_{m}$ and $\mathcal{D}_{m}$ (where $m$ is either
$\mathcal{A}$ or $\mathcal{B}$). 
More concretely,
$\mathcal{E}_{m}(c)$ returns a pair of two string $b_{1}$ and $b_{2}$
 with the property that
$\mathcal{D}_{m}(b_{1}, b_{2}) = c$. We assume that the underlying \mpc
protocol instantiates $\mathcal{E}_{m}$ and $\mathcal{D}_{m}$
appropriately. For ABY protocol \cite{aby}, algorithms $(\mathcal{E}_{\mathcal{A}},\mathcal{D}_{\mathcal{A}})$ (resp. $(\mathcal{E}_{\mathcal{B}},\mathcal{D}_{\mathcal{B}})$) correspond to the arithmetic (resp. boolean) sharing and reconstruction algorithms.

\figureref{cktsem} gives the judgements for evaluation of circuit by the two parties using the \mpc protocol. The circuit environment for party $j$ is defined as follows:

\vspace{0.2cm}
$
\small
\begin{array}{rrcl}
    \ftext{Circuit environment} & \widehat\rho_j &::=& \cdot \mid \widehat\rho_j,\wire \mapsto b_j\\
\end{array}
$
\vspace{0.2cm}

\divya{strings $b$ are not formally defined.}

We give the 
judgments $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \gate
\Downarrow b_{1}, b_{2}$, and $\widehat{\rho}_{1}, \widehat{\rho}_{2}
\vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O$,
where $O$ are the observations (similar to source semantics). 
Rule ({\sc{C-In}}) is used to evaluate the input gate $\kw{in}^{m}_{j}$ that creates the $m$ type shares of the value $c$ input by party $j$.
Rule ({\sc{C-Mult}}) evinces the pattern for evaluating circuit
gates $\gate$. To evaluate $\kw{mult}\:\gate_{1}\:\gate_{2}$, the
rule first evaluates $\gate_{1}$ to $(b_{11}, b_{21})$ and
$\gate_{2}$ to $(b_{12}, b_{22})$. Shares $(b_{11}, b_{21})$ are then
combined using $\mathcal{D_{\mathcal{A}}}$ to $n_{1}$, and similarly
$(b_{12}, b_{22})$ are combined to $n_{2}$. The final output of the
\kw{mult} gate is then $\mathcal{E}_{\mathcal{A}}(n_{1} \mulop n_{2})$. Note
that this is a functional description of how the \kw{mult} gate
evaluates, of course, concretely $n_{1}$ and $n_{2}$ are not observed
by the parties. Rule ({\sc{C-Coerce}}) creates the shares using the
scheme for $m$. Coming to the evaluation of circuits, the evaluation
of \kw{bind} updates the mapping of $\wire$ in the input environments, and
the rule ({\sc{C-Out}}) outputs the clear value $c$ to the
observations.

@@

    \inferrule*[lab={\footnotesize{C-Out}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m}(b_{1}, b_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{out}\:\gate \Downarrow \widehat{\rho_{1}}, \widehat{\rho_{2}}; c
               }
\end{array}
  \]
\caption{Circuit semantics (selected rules)}
\label{fig:cktsem}
\end{figure}

\subsubsection*{Correctness theorem} We first define a judgment for
translation of environments, $\Gamma \vdash \rho \leadsto
\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
judgment is defined inductively on $\Gamma$, and establishes that
the static environment $\Gamma$ is consistent with the runtime
environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
$\widehat{\rho}_{2}$. As an example, if $x:\kw{uint}^{\mathcal{P}} \in
\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
n$, for some $n$. \divya{This judgement is not clear. If I am correct, it says that for public values $\rho$ and $\widetilde{\rho}$ are consistent and for secret values $\rho$ has values and $\widehat{rho}_j$ contain shares.} We elide the judgment, providing the full definition
in the supplementary material.

With this judgment in hand, the correctness theorem is as follows:

\begin{theorem}[Correctness]\label{theorem:correctness}
  $\forall\:\Gamma, s, \widetilde{s}, \Gamma_{1}, \rho, \widetilde{\rho}, \widehat{\rho}_{1}, \widehat{\rho}_{2}$, if:

  \begin{enumerate}
  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
  \end{enumerate}

  then $\exists \rho_{1}, O_{1}, \widetilde{\rho}_{1}, \chi, \widehat{\rho}'_{1}, \widehat{\rho}'_{2}, O_{2}$, s.t.

  \begin{enumerate}[label=(\alph*)]
  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
  \item $O_{1} = O_{2}$
  \end{enumerate}

\end{theorem}

The theorem states that if a source statement $s$ is well-typed, and
compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
Furthermore, the final environments are also in the compilation
relation. \divya{Should we call the judgement between environs as compilation relation?}
Due to space reasons, we provide the proof in \cite{anonymized}.

>>>>

Most of the expression forms $\widetilde{e}$ are same as $e$, except
that the binary operators, and the conditional forms
are annotated with labels $\ell$.
Looking ahead, the label determines how the operators are
evaluated: $\mathcal{P}$-labeled operators are evaluated in-clear, $\mathcal{A}$-labeled operators generate arithmetic circuits, and
$\mathcal{B}$-labeled operators generate boolean circuits. The
form $\widetilde{e} \rhd m$ denotes coercing $\widetilde{e}$ to the label $m$, which generates conversions to $m$. 
%The statements $\widetilde{s}$ are analogous to $s$.

@@

As mentioned earlier, the intermediate language models the code such as in \figureref{ex-aby} output by our compiler. 
Next, a program in the intermediate language is evaluated to a circuit that can be executed in the distributed setting later. The evaluation to a circuit computes away the public parts of the program and also \emph{flattens} the arrays so that the circuits are unaware of the array structure. 
Crucially, this phase of the semantics does not have access to the secret inputs.
Below, we first provide the language for the circuits used followed by our evaluation rules.

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{mult}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \gate \rhd m \mid c\\
    \ftext{Sub-circuit} & \val & ::= & \gate \mid [\overline{\gate_{i}}]_{n}\\
    %\ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits  syntax}
\label{fig:circuits}
\end{figure}

@@

    \inferrule*[lab={\footnotesize{S-Read}}]
               {
                 \widetilde{\rho} \vdash x \Downarrow [\overline{\wire_i}]_{n_{1}} \\\\
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow n \quad n < n_{1}
               }
               {
                 \widetilde{\rho} \vdash x[\widetilde{e}] \Downarrow \wire_n
               }\\\\
    \inferrule*[lab={\footnotesize{S-SMult}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \gate_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} \mulop_{\mathcal{A}} \widetilde{e_{2}} \Downarrow \kw{mult}\:\gate_{1}\:\gate_{2}
               }

@@

\subsubsection*{Evaluation to Circuits}
\figureref{circuits} shows the syntax of circuits. A wire id range
$\wire$ denotes a set of circuit wires that carry the runtime value of a
 variable with a secret label (we will concretely define these runtime
values later as part of the circuit semantics). Circuit gates $\gate$
are $\wire$, input gates, \kw{mult}, \kw{gt}, and \kw{mux} gates, 
coerce gates $\gate \rhd m$, and constant gates.  Sub-circuits $\val$ 
(generated from $\widetilde e$)
then consist of gates and arrays of gates.

 \figureref{eval-inter-circ} shows the judgments for the evaluation of the intermediate language to a circuit. 
The runtime environment maps variables to sub-circuits and is defined as follows:

\vspace{0.2cm}
$
\small
\begin{array}{rrcl}
    \ftext{Runtime environment} & \widetilde\rho &::=& \cdot \mid \widetilde\rho,x \mapsto \val\\
\end{array}
$
\vspace{0.2cm}

We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow\val$. 
%
Rules ({\sc{S-PMult}}) and ({\sc{S-SMult}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PMult}}) evaluates a public multiplication $\widetilde{e_{1}}
\mulop_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} \mulop n_{2}$, similar to the
source semantics of \figureref{srcsem}. In contrast, the rule
({\sc{S-SMult}}) evaluates a secret multiplication $\widetilde{e_{1}}
\mulop_{\mathcal{A}} \widetilde{e_{2}}$ to an arithmetic multiplication
gate $\kw{mult}\:\gate_{1}\:\gate_{2}$. As mentioned above, the intermediate language
expressions generated by our compiler never have $\widetilde{e_{1}}
\mulop_{\mathcal{B}} \widetilde{e_{2}}$, as our compiler is aware that $\mulop$
is more performant using an arithmetic circuit compared to a boolean
one~\cite{aby}. Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the value from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a multiplexer \kw{mux} gate that takes input
circuits from the guard ($\gate_{1}$) and both the branches
($\gate_{2}$ and $\gate_{3}$). Once again for performance reasons,
the target expressions from our compiler do not have
$\lcond{\mathcal{A}}{e_{1}}{e_{2}}{e_{3}}$. Rules
({\sc{S-Coerce}}) and ({\sc{S-Inp}}) evaluate to coerce and input
gates respectively.

Statement evaluation $\widetilde{\rho} \vdash \widetilde{s} \Downarrow
\widetilde{\rho}_{1}; \chi$ evaluates a statement $\widetilde{s}$ under 
the environment $\widetilde{\rho}$  to produce a new
environment $\widetilde{\rho}_{1}$, and a circuit $\crct$. A circuit $\crct$ (shown
in \figureref{circuits}) is either empty, \kw{bind}-ing of a
circuit gate $\gate$ to wire $\wire$, \kw{out} gate, or a sequence of
circuits. Rules ({\sc{S-DeclC}}), ({\sc{S-DeclCkt}}), and
({\sc{S-DeclCktA}}) show the variable declaration cases. Rule
({\sc{S-DeclC}}) shows the case when $\widetilde{e}$ evaluates to
$\val$, where $\val$ is either a constant or an
array of constants. In this case, the mapping $x \mapsto
\val$ is added to the environment, and the resulting circuit
is empty. When 
$\widetilde{e}$ evaluates to a circuit $\gate$, rule
({\sc{S-DeclCkt}}) picks a fresh wire $\wire$, adds the mapping $x \mapsto \wire$
to the environment $\widetilde{\rho}$, and outputs the circuit
$\kw{bind}\:\gate\:\wire$. Rule ({\sc{S-DeclCktA}}) is analogous for
$\widetilde{e}$ evaluating to an array of circuits. The variable
assignment rules (not shown in the figure) are similar. Rule
({\sc{S-WriteCkt}}) shows the case for writing to an array, where the
array contents are secret. Finally, rule ({\sc{S-Out}}) compiles to an
\kw{out} circuit.

\subsubsection*{Circuit semantics} Evaluating a program in the intermediate language produces a
circuit over the secret data to be computed using a \mpc protocol in the distributed setting. With
our runtime circuit semantics, we model the \emph{functional} aspect of a \mpc protocol, parametrized by cryptographic encoding and decoding functions.

During the circuit evaluation, the wire ranges $r$ are
mapped to (random) strings $b$. The semantics of these strings is
given by pairs of encode-decode algorithms, written as
$\mathcal{E}_{m}$ and $\mathcal{D}_{m}$ (where $m$ is either
$\mathcal{A}$ or $\mathcal{B}$). 
More concretely,
$\mathcal{E}_{m}(c)$ returns a pair of two strings $b_{1}$ and $b_{2}$
 with the property that
$\mathcal{D}_{m}(b_{1}, b_{2}) = c$. 
The string $b_i$ denotes the $i^{th}$ party's {\it share} of $c$.
We assume that the underlying \mpc
protocol instantiates $\mathcal{E}_{m}$ and $\mathcal{D}_{m}$
appropriately. For ABY protocol \cite{aby}, algorithms $(\mathcal{E}_{\mathcal{A}},\mathcal{D}_{\mathcal{A}})$ (resp. $(\mathcal{E}_{\mathcal{B}},\mathcal{D}_{\mathcal{B}})$) correspond to the arithmetic (resp. boolean) sharing and reconstruction algorithms.

\figureref{cktsem} gives the judgements for evaluation of circuits by the two parties using the \mpc protocol. The circuit environment  is a map from wires to shares and is defined as follows:

\vspace{0.2cm}
$
\small
\begin{array}{rrcl}
    \ftext{Circuit environment} & \widehat\rho &::=& \cdot \mid \widehat\rho,\wire \mapsto b\\
\end{array}
$
\vspace{0.2cm}

We use $\widehat\rho_j$ to denote the circuit environment for party $j.$ 
We give the 
judgments $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \gate
\Downarrow b_{1}, b_{2}$, and $\widehat{\rho}_{1}, \widehat{\rho}_{2}
\vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O$,
where $O$ are the observations (similar to source semantics). 
Rule ({\sc{C-In}}) is used to evaluate the input gate $\kw{in}^{m}_{j}$ that creates the $m$ type shares of the value $c$ input by party $j$.
Rule ({\sc{C-Mult}}) evinces the pattern for evaluating circuit
gates $\gate$. To evaluate $\kw{mult}\:\gate_{1}\:\gate_{2}$, the
rule first evaluates $\gate_{1}$ to $(b_{11}, b_{21})$ and
$\gate_{2}$ to $(b_{12}, b_{22})$. Shares $(b_{11}, b_{21})$ are then
combined using $\mathcal{D_{\mathcal{A}}}$ to $n_{1}$, and similarly
$(b_{12}, b_{22})$ are combined to $n_{2}$. The final output of the
\kw{mult} gate is then $\mathcal{E}_{\mathcal{A}}(n_{1} \mulop n_{2})$. Note
that this is a functional description of how the \kw{mult} gate
evaluates, of course, concretely $n_{1}$ and $n_{2}$ are not observed
by the parties. Rule ({\sc{C-Coerce}}) creates the shares using  $\mathcal{E}_m$. The evaluation
of \kw{bind} updates the mapping of $\wire$ in the input environments, and
the rule ({\sc{C-Out}}) outputs the clear value $c$ to the
observations.

@@

    \inferrule*[lab={\footnotesize{C-Out}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m}(b_{1}, b_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{out}\:\gate \Downarrow \widehat{\rho_{1}}, \widehat{\rho_{2}}; c
               }
\end{array}
  \]
\caption{Circuit semantics in a distributed runtime(selected rules)}
\label{fig:cktsem}
\end{figure}

%\subsubsection*{Correctness theorem}
Finally, the correctness theorem is as follows (the environments on the left of $\vdash$ are empty and we elide the environments on the right of $\vdash$ for brevity):

\begin{theorem}[Correctness]\label{theorem:correctness}
 $\forall\: s, \widetilde{s}$, if $\vdash s \leadsto \widetilde{s} \mid \_$  then $\exists  O , \chi$, s.t.  $\vdash s \Downarrow \_; O$, $ \vdash \widetilde{s} \Downarrow \_; \chi$, and $ \vdash \chi \Downarrow \_, \_; O$  
\end{theorem}

The theorem states that if a source statement $s$ is well-typed, and
compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
semantics with observations $O$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
circuit semantics with the same observations $O$. 
Therefore, well typed programs always terminate (array indices are always in bounds, there are no unbounded loops, etc.) and the protocol produces the same outputs as the source semantics.
% We first define a judgment for
%translation of environments, $\Gamma \vdash \rho \leadsto
%\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
%judgment is defined inductively on $\Gamma$, and establishes that
%the static environment $\Gamma$ is consistent with the runtime
%environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
%$\widehat{\rho}_{2}$. 
%As an example, if $x:\kw{uint}^{\mathcal{P}} \in
%\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
%n$, for some $n$. On the other hand, if $x:\kw{uint}^{m} \in
%\Gamma$ then the judgement checks that $\mathcal{D}_m( \widehat{\rho}_{1}(\widetilde{\rho}(x)),\widehat{\rho}_{2}(\widetilde{\rho}(x)))=\rho(x)$.
%%We elide the judgment, providing the full definition
%%in the supplementary material.
%With this judgment,
%the correctness theorem is as follows:
%
%\begin{theorem}[Correctness]\label{theorem:correctness}
%  $\forall\:\Gamma, s, \widetilde{s}, \Gamma_{1}, \rho, \widetilde{\rho}, \widehat{\rho}_{1}, \widehat{\rho}_{2}$, if:
%
%  \begin{enumerate}
%  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
%  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
%  \end{enumerate}
%
%  then $\exists \rho_{1}, O_{1}, \widetilde{\rho}_{1}, \chi, \widehat{\rho}'_{1}, \widehat{\rho}'_{2}, O_{2}$, s.t.
%
%  \begin{enumerate}[label=(\alph*)]
%  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
%  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
%  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
%  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
%  \item $O_{1} = O_{2}$
%  \end{enumerate}
%  
%\end{theorem}
%
%The theorem states that if a source statement $s$ is well-typed, and
%compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
%semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
%circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
%%Furthermore, the final environments are also in the compilation
%%relation. \divya{Should we call the judgement between environs as compilation relation?}
%Due to space reasons, we provide the proof in \cite{anonymized}.
